A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-09-11 plots/cifar/aft_comparison.tex

\begin{table*}
\centering
\caption{Comparison of AFT Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -5.18e+03 & -5.19e+03 & 0.85 & 0.86 & 0 & 0 & 0 & 0 \\
Cox & -- & -- & 0.85 & 0.86 & 0.02 & 0.02 & 0 & 0 \\
Log Logistic & -5.42e+03 & -5.43e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -5.57e+03 & -5.58e+03 & 0.84 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFT Models on the CIFAR dataset.}
\label{tab:cifar}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -8.7e+03 & -8.7e+03 & 0.83 & 0.84 & 0 & 0 & 0 & 0 \\
Cox & -- & -- & 0.83 & 0.84 & 0.02 & 0.02 & 0 & 0 \\
Log Logistic & -9.18e+03 & -9.18e+03 & 0.83 & 0.84 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -9.43e+03 & -9.43e+03 & 0.83 & 0.84 & 0.01 & 0.01 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-09-11 plots/combined/aft_comparison.tex
++plots
linting

\begin{table*}
\centering
\caption{Comparison of AFR Models on the combined dataset.}
\label{tab:combined}
\begin{tabular}{lrrrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -2.11e+04 & -2.11e+04 & 0.84 & 0.83 & 0 & 0.01 & 0 & 0 \\
Log Logistic & -2.18e+04 & -2.18e+04 & 0.84 & 0.83 & 0.01 & 0.01 & 0 & 0 \\
Log Normal & -2.25e+04 & -2.25e+04 & 0.84 & 0.83 & 0.01 & 0 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFT Models on the combined dataset.}
\label{tab:combined}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -1.87e+04 & -1.87e+04 & 0.85 & 0.84 & 0 & 0.01 & 0 & 0 \\
Cox & -- & -- & 0.85 & 0.84 & 0.01 & 0.01 & 0 & 0 \\
Log Logistic & -1.9e+04 & -1.9e+04 & 0.85 & 0.84 & 0.02 & 0.01 & 0 & 0 \\
Log Normal & -1.98e+04 & -1.98e+04 & 0.85 & 0.85 & 0.01 & 0.01 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

### 2024-09-11 plots/mnist/aft_comparison.tex

\begin{table*}
\centering
\caption{Comparison of AFT Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -6.51e+03 & -6.51e+03 & 0.9 & 0.9 & 0.01 & 0.02 & 0 & 0 \\
Cox & -- & -- & 0.9 & 0.9 & 0.04 & 0.04 & 0 & 0 \\
Log Logistic & -6.48e+03 & -6.48e+03 & 0.91 & 0.9 & 0.03 & 0.04 & 0 & 0 \\
Log Normal & -6.63e+03 & -6.63e+03 & 0.91 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}

>>>>

\begin{table*}
\centering
\caption{Comparison of AFT Models on the MNIST dataset.}
\label{tab:mnist}
\begin{tabular}{lllrrrrrr}
\toprule
 & AIC & BIC & Concordance & Test Concordance & ICI & Test ICI & E50 & Test E50 \\
\midrule
Weibull & -1.05e+04 & -1.05e+04 & 0.89 & 0.9 & 0.01 & 0.02 & 0 & 0 \\
Cox & -- & -- & 0.89 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
Log Logistic & -1.07e+04 & -1.07e+04 & 0.89 & 0.9 & 0.03 & 0.03 & 0 & 0 \\
Log Normal & -1.09e+04 & -1.09e+04 & 0.89 & 0.9 & 0.02 & 0.02 & 0 & 0 \\
\bottomrule
\end{tabular}
\end{table*}
